---
title: "IODS-final"
author: 
- Heidi Maanonen
- heidi.maanonen@helsinki.fi
date: "26.2.2017"
output: 
  html_document:
    theme: sandstone
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: true
    toc_depth: 2
    fig_caption: true
    fig_width: 6
    fig_height: 4
    code_folding: hide
---

&nbsp;

# The purpose of the final work

&nbsp;

The idea of the this final work is to show and demonstrate what I have been learning about R, data visualizing and statistics during this course called **Introduction to Open Data Science**. The course is organized by [University of Helsinki](https://wiki.helsinki.fi/display/SocStats/Introduction+to+Open+Data+Science,+spring+2017). I really want highlight that this was and is my first course and work with R programming. Considering this I like to believe that I have learnt a lot of very interesting ways of using R, RStudio and Rpackages.

In this final work We have 2 options of choosing our data. First we could use one of the the datasets which we had already applied. Alternatively we could try to find a new dataset from internet in terms of our interests or just to raise the degree of difficulty, I think. And because I'm very interested in research I wanted to find a new dataset to learn how to do the whole data wrangling and exploring process by myself. 

My intention here is to deepen my knowledge on [Principal Component Analysis](https://en.wikipedia.org/wiki/Principal_component_analysis) in terms of finding some latent structure of the dataset introduced in the next chapter.  

&nbsp;

# Description of the dataset

&nbsp;


I choose the dataset from [Kaggle](https://www.kaggle.com/miroslavsabo/young-people-survey), which is about **Preferencies, interests, habits, opinions and fears of young people** in Slovakia. In 2013, students of the Statistics class at [FSEV UK](https://fses.uniba.sk/en/) were asked to invite their friends to participate in this survey. Accordingly they managed to get 1 010 participants for this purpose. 

If you take a look at the Kaggle link you can see that there are huge amount of variables, that is 150 columns mainly integers but also some categorical variables. Thus for the purpose of this assignment and Principal Component Analysis I had to choose some interesting content which is funny because I choose the interests and hobbies of these young people. In addition, I also wanted to count in some demographical variables to make visualizations more versatile.

&nbsp;

## First part of data wrangling 

&nbsp;


You can find all of the datasets from my [GitHub Repository](https://github.com/8475394/IODS-final/tree/master/Data). The CSV-file called "raw_young_people_survey" is the original dataset from Kaggle. The "create_interests.R" is the R Script file of my data wrangling and the "interests_dem.txt" is the file what I'm going to use here.

&nbsp;

<p class="text-warning">BRIEF DESCRIPTION OF DATA WRANGLING PHASES:</p>

1. Reading the whole dataset
2. Selecting the variables of interests and hobbies including age and gender
3. Renaming some variables
4. Exploring missing values
5. Removing the rows with missing values
6. Saving the new data


&nbsp;

## Introducing the variables 

&nbsp;

From the structure table below you see that after data wrangling part there are 878 observation and 34 variables, mostly integers, i.e. continuous variables and 1 factor variable. The first 32 variables represent different interests and hobbies of young people which were measured on the [Likert Scale](https://en.wikipedia.org/wiki/Likert_scale) from 1 to 5 (Not interested - Very interested). Last two variables contains information about age and gender, where the former varies between 15 and 30 years. The latter contains categories of female and male.

Some of these variables may need some additional information, thus I made a table for their longer and short names. However, most of the variables have same longer and shorter name. See the table after exploring the structure of the data.

&nbsp;

<p class="text-warning">DATA STRUCTURE</p>


```{r, message=FALSE, warning=FALSE}
# Reading the data with interests and demographics
interests_dem <- read.table(file.path("C:/Users/heidi/Documents/YLIOPISTO/TILASTOTIEDE/INTRODUCTION TO OPEN DATA SCIENCE/IODS-final/data", "interests_dem.txt"), header = TRUE)

# Printing the data structure
library(dplyr)
glimpse(interests_dem)
```


&nbsp;

<p class="text-warning">INTERESTS AND THEIR SHORT NAMES</p> 

&nbsp;


INTEREST        | Short name          | INTEREST    | Short name
----------------|---------------------|-------------|-------------
1. History           | History        | 18. Religion     | Religion
2. Psychology        | Psychology     | 19. Outdoor activities | Outdoor
3. Politics          | Politics       | 20. Dancing     | Dancing
4. Mathematics       | Mathematics    | 21. Playing musical instruments | Instruments
5. Physics           | Physics        | 22. Poetry writing | wPoetry
6. Internet          | Internet       | 23. Sport and leisure activities | sLeisure
7. PC Software, Hardware| PC          | 24. Sport at competitive level | sCompetitive
8. Economy, Management | Economy      | 25. Gardening | Gardening
9. Biology           | Biology        | 26. Celebrity lifestyle | Celebrities
10. Chemistry         | Chemistry     | 27. Shopping | Shopping
11. Poetry reading    | rPoetry       | 28. Science and technology | SciTec
12. Geography         | Geography     | 29. Theatre | Theatre
13. Foreign languages | Languages     | 30. Socializing with friends | Social
14. Medicine          | Medicine      | 31. Adrenaline sports | sAdrenaline
15. Law               | Law           | 32. Pets | Pets
16. Cars              | Cars          | 33. Age | Age
17. Art exhibitions   | Art           | 34. Gender | Gender


&nbsp;

## Summary tables 

&nbsp;

The dataset contains a lot of variables, also producing many summary tables. 

As you can perceive, all of the variables, besides age, varies between 1 and 5. This means that the whole scale has been used considering each of the variables, besides age. Interestingly, some distributions are quite flat, suggesting average interest toward the hobbies or interests. By this I mean that the mean and median values are around 3. These include **History, Psychology, PC, Poetry reading, Geography, Sport at competitive level, Shopping, Science and technology, Theatre and  Adrenaline sports**.  

Then there are some variables with quite low average interest, including for example **Physics, Chemistry, Poetry writing and Gardening** and very high interest, including **Internet, Languages, Outdoor activities and Socializing with friends**. 

When exploring the distributions, it is good to remember that the participants were not just the students but also their friends. This means that the participants can come from the University, working life, etc.   



```{r, fig.width=10, message=FALSE, warning=FALSE, results='asis'}
library(knitr); library(dplyr)
kable(summary(interests_dem[,1:7]), format = "pandoc", digits = 2,  caption = 'Summary 1', align = "l")

kable(summary(interests_dem[,8:14]), format = "pandoc", digits = 2,  caption = 'Summary 2', align = "l")

kable(summary(interests_dem[,15:21]), format = "pandoc", digits = 2,  caption = 'Summary 3', align = "l")

kable(summary(interests_dem[,22:28]), format = "pandoc", digits = 2,  caption = 'Summary 4', align = "l")

kable(summary(interests_dem[,29:33]), format = "pandoc", digits = 2,  caption = 'Summary 5', align = "l")


```

&nbsp;

<p class="text-warning">SUMMARY OF GENDER</p> 

This last tiny table informs us that there are 520 females and 358 males.


```{r}
Gender <- interests_dem$Gender
table(Gender)
```


&nbsp;

# Reasearch problem and initial hypotheses

&nbsp;

The research problem is to reduce the dimensions of the data by **young people's interests and hobbies** and identify and express a meaningful pattern of components in terms of clarity and exploratory fashion. First I offer some general backround information of my initial proposal and after this I present the initial hypotheses or proposal together with the colored histograms.

In this section you can see the ditributions more visually. The coloring might seem confucing at first but there is actually a strategy behind this. As I mentioned earlier, my intention is to deepen my knowledge in terms of Principal Component Analysis (PCA), hence the coloring points to **initial proposal** of the latent structure inside the data. I'm highlighting the word initial because the structure is based partially on my personal intuition and partially on the "behaviour" of the distributions. Additionally, I want to form my perception of the structure from beginning to end, rather than perform the statistical methods first and then look back and write these chapters. Thus I could call this as my learnings process.

Note that the histograms are showed regarding the original variable list while the structure is organized by proposed groups or components. Note also that gender as well as the ditribution of age are visualized only for the imformative purposes.


&nbsp;

## Initial proposal of latent structure and hypotheses

&nbsp;

<p class="text-warning">FIRST DIMENSION</p> 

In the beginning I maybe wouldn't have chosen the psychology here but I think it's important that these variables share somewhat similar distributions. If these variables belong to same component, the dimension could be called something like **interest toward base disciplines of cultural characteristics with respect to human beings**.

* History
* Psychology
* Geography

&nbsp;

<p class="text-warning">SECOND DIMENSION</p>

Also this dimension contains variables with somewhat equivalent distributions and I think they share some common parts of **intellectual elements**.

* Politics      
* Economy, management
* Biology       
* Medicine
* Art exhibition

&nbsp;

<p class="text-warning">THIRD DIMENSION</p>

This dimension is a bit tricky. To me, it makes sense that the math, physics and chemistry could belong to the same scope. The variable of being interest toward law is more complicated. It could belong here or to the earlier dimension of "intellectual features". In terms of this third dimension the content of law contains a lot of details and complex attributes as well as math, physics and chemistry. Thus, if a person is interested in putting effort **to calculate details and logical problems**, this dimension can make sense (so far). 

* Mathematics
* Physics
* Chemistry
* Law

Then, my intention at first was to create one more dimension for variables below until I noticed that their distribution is likely to be similar with the above variables. First I thought that religion, playing instruments, poetry writing and gardening relate to some artistic features which still could be the explanation. But according to the information of similarities in their distributions, it could be "true" that some people are interested in all of these contents. There might be a situation that **people interested in math, physics, chemistry and law would like to have some counterbalance hobbies or worldview in terms of religion**. However, it is not very easy to figure out a name representing all these variables, thus I think I need to ensure the results first. 

* Religion
* Playing musical instruments
* Poetry writing
* Gardening

&nbsp;

<p class="text-warning">FOURTH DIMENSION</p>

At this point, the fourth dimension contains the futher variables:

* Internet
* Foreign languages
* Outdoor activities
* Sport and leisure activities
* Sport at competitive level
* Socializing with friends
* Pets

There is more variablity in this dimension considering the distributions. However, I think that all these variables share some **interest toward socializing** with one way or other. 

&nbsp;

<p class="text-warning">FIFTH DIMENSION</p>

I think that this dimension contains at least PC and interest toward science and techology, since PC can be considered as technology. This can be true also in terms of cars but its ditribution doesn't fit. Finally it seems that the Andrenaline sports doesn't fit nowhere. Nevertheless, if it belongs here, the dimension could be called for example **interest toward speed and technology**.

* PC
* Science and technology
* Cars
* Adrenaline sports

&nbsp;

<p class="text-warning">SIXTH DIMENSION</p>

These variables can be close with socializing aspects regarding their actual content or meaning. However their distributions seem to somewhat different and for that reason I separated the variables below as their own dimension. It seems that within this data, these interests are more important to women than men, which could be the common nominator. Hope nobody gets hurt if I call these as **feminine activities**. 

* Poetry reading
* Shopping
* Theatre


&nbsp;

<p class="text-warning">SEVENTH DIMENSION</p>

This last dimension may contain the following variables:

* Dancing
* Celebrity lifestyle

I think that these share the most obvious relationship regarding their content but let's see later if the PCA agrees with me.

&nbsp;

## Histograms considering the latent structure

&nbsp;


```{r, fig.height=9, fig.width=10, message=FALSE, warning=FALSE}
library(ggplot2); library(gridExtra)

# Nice  plave to learn about ggplot: https://sesync-ci.github.io/graphics-with-ggplot2-lesson/2016/08/25/
# Palettes and colors: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#palettes-color-brewer 

h1 <- ggplot(interests_dem, aes(interests_dem$History, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("orangered", "forestgreen")) + theme(legend.position=c(0.11, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward history") + xlab("History")

h2 <- ggplot(interests_dem, aes(interests_dem$Psychology, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("orangered", "forestgreen")) + theme(legend.position=c(0.11, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward psychology") + xlab("Psychology")

h3 <- ggplot(interests_dem, aes(interests_dem$Politics, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF6666", "#66CC99")) + theme(legend.position=c(0.9, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward politics") + xlab("Politics")

h4 <- ggplot(interests_dem, aes(interests_dem$Mathematics, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward mathematics") + xlab("Mathematics")

h5 <- ggplot(interests_dem, aes(interests_dem$Physics, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward physics") + xlab("Physics")

h6 <- ggplot(interests_dem, aes(interests_dem$Internet, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.18, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward Internet") + xlab("Internet")

h7 <- ggplot(interests_dem, aes(interests_dem$PC, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("darkorange", "#CC6600")) + theme(legend.position=c(0.11, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward PC") + xlab("PC")

h8 <- ggplot(interests_dem, aes(interests_dem$Economy, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF6666", "#66CC99")) + theme(legend.position=c(0.85, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward economy") + xlab("Economy, Management")

h9 <- ggplot(interests_dem, aes(interests_dem$Biology, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF6666", "#66CC99")) + theme(legend.position=c(0.85, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward biology") + xlab("Biology")

grid.arrange(h1, h2, h3, h4, h5, h6, h7, h8, h9, ncol = 3, nrow =3)
```

&nbsp;


```{r, fig.height=9, fig.width=10, message=FALSE, warning=FALSE}
library(ggplot2); library(gridExtra)

h10 <- ggplot(interests_dem, aes(interests_dem$Chemistry, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.85, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward chemistry") + xlab("Chemistry")

h11 <- ggplot(interests_dem, aes(interests_dem$rPoetry, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF0000", "blue")) + theme(legend.position=c(0.4, 0.9), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward rPoetry") + xlab("Poetry reading")

h12 <- ggplot(interests_dem, aes(interests_dem$Geography, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("orangered", "forestgreen")) + theme(legend.position=c(0.11, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward geography") + xlab("Geography")

h13 <- ggplot(interests_dem, aes(interests_dem$Languages, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.2, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward languages") + xlab("Foreign languages")

h14 <- ggplot(interests_dem, aes(interests_dem$Medicine, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF6666", "#66CC99")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward medicine") + xlab("Medicine")

h15 <- ggplot(interests_dem, aes(interests_dem$Law, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward law") + xlab("Law")

h16 <- ggplot(interests_dem, aes(interests_dem$Cars, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("darkorange", "#CC6600")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward cars") + xlab("Cars")

h17 <- ggplot(interests_dem, aes(interests_dem$Art, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF6666", "#66CC99")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward art") + xlab("Art exhibitions")

h18 <- ggplot(interests_dem, aes(interests_dem$Religion, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward religion") + xlab("Religion")

grid.arrange(h10, h11, h12, h13, h14, h15, h16, h17, h18, ncol = 3, nrow =3)
```


&nbsp;


```{r, fig.height=9, fig.width=10, message=FALSE, warning=FALSE}
library(ggplot2); library(gridExtra)

h19 <- ggplot(interests_dem, aes(interests_dem$Outdoor, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.2, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward outdoor") + xlab("Outdoor activities")

h20 <- ggplot(interests_dem, aes(interests_dem$Dancing, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("tan1", "greenyellow")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward dancing") + xlab("Dancing")

h21 <- ggplot(interests_dem, aes(interests_dem$Instruments, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward instruments") + xlab("Playing musical instruments")

h22 <- ggplot(interests_dem, aes(interests_dem$wPoetry, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward wPoetry") + xlab("Poetry writing")

h23 <- ggplot(interests_dem, aes(interests_dem$sLeisure, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.2, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward sLeisure") + xlab("Sport and leisure activities")

h24 <- ggplot(interests_dem, aes(interests_dem$sCompetitive, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.3, 0.85), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward sCompetitive") + xlab("Sport at competitive level")

h25 <- ggplot(interests_dem, aes(interests_dem$Gardening, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#CC79A7", "#0072B2")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward gardening") + xlab("Gardening")

h26 <- ggplot(interests_dem, aes(interests_dem$Celebrities, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("tan1", "greenyellow")) + theme(legend.position=c(0.82, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward Celebrities") + xlab("Celebrity lifestyle")

h27 <- ggplot(interests_dem, aes(interests_dem$Shopping, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF0000", "blue")) + theme(legend.position=c(0.11, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward shopping") + xlab("Shopping")

grid.arrange(h19, h20, h21, h22, h23, h24, h25, h26, h27, ncol = 3, nrow =3)
```


&nbsp;

```{r, fig.height=6, fig.width=10, message=FALSE, warning=FALSE}
library(ggplot2); library(gridExtra)


h28 <- ggplot(interests_dem, aes(interests_dem$SciTec, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("darkorange", "#CC6600")) + theme(legend.position=c(0.11, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward SciTec") + xlab("Science and technology")

h29 <- ggplot(interests_dem, aes(interests_dem$Theatre, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("#FF0000", "blue")) + theme(legend.position=c(0.11, 0.85), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward theatre") + xlab("Theatre")

h30 <- ggplot(interests_dem, aes(interests_dem$Social, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.2, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward socializing") + xlab("Socializing with friends")

h31 <- ggplot(interests_dem, aes(interests_dem$sAdrenaline, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("darkorange", "#CC6600")) + theme(legend.position=c(0.9, 0.15), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward sAdrenaline") + xlab("Adrenaline sports")

h32 <- ggplot(interests_dem, aes(interests_dem$Pets, fill = Gender)) + geom_histogram(binwidth = 1, color = "white", alpha = 0.8) + scale_fill_manual(values=c("yellow", "dimgray")) + theme(legend.position=c(0.2, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Interest toward pets") + xlab("Pets")

h33 <- ggplot(interests_dem, aes(interests_dem$Age, fill = Gender)) + geom_histogram(binwidth = 2, color = "white", alpha = 0.8) + scale_fill_manual(values=c("pink", "skyblue")) + theme(legend.position=c(0.8, 0.8), legend.title=element_text(size=8), legend.text = element_text(size = 8)) + ggtitle("Age of participants") + xlab("Age")

grid.arrange(h28, h29, h30, h31, h32, h33, ncol = 3, nrow =2)
```

&nbsp;


&nbsp;